Listings of equations, figures, tables and sections of the article '{\it \bf Musical elements in the discrete-time representation of sound}' and of the scripts in the MASS toolbox

### 2017-09-22 article/acm/listings.tex
temporal brench to move changes to other lap

@@

\author{\\\\\\ Renato Fabbri (USP),\\
Vilson Vieira da Silva Junior (The Grid),\\
Ant\^onio Carlos Silvano Pessotti (Unimep),\\
D\'ebora Cristina Corr\^ea,\\
Osvaldo N. Oliveira Jr. (USP)
}

@@

\clearpage
\section{Figures}

@@

\clearpage
\section{Scripts}
\subsection{For all equations in each chapter}
\clearpage
\subsection{To render musical pieces}
\clearpage
\subsection{To render the figures used in the article}

\clearpage
\section{Other documents}
Latex files. PDF files.
MSc Dissertation.

\section{Final considerations}

>>>>

\newcommand*{\reff}[1]{%
	{\NoHyper\ref{#1}\endNoHyper}%
	  }

@@

\author{\\\\\\ Renato Fabbri (USP),\\
Vilson Vieira da Silva Junior (Cod.ai),\\
Ant\^onio Carlos Silvano Pessotti (Unimep),\\
D\'ebora Cristina Corr\^ea,\\
Osvaldo N. Oliveira Jr. (USP)
}

@@

\begin{table*}[htp!]
\centering
\caption{Equation numbers and their descriptions.
All these equations are implemented in file \texttt{src/sections/2.py}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{eq:dur} & relation between number of samples and duration \\
 \reff{eq:potencia} & power of the wave \\
 \reff{decibels} & decibels by difference by means of the power of each wave \\
 \reff{eq:ampVol} & double amplitude implies $\approx 6dB$ \\
 \reff{eq:potVol} & double power implies $\approx 3dB$ \\
 \reff{eq:dobraVol} & double volume ($10dB$) implies a factor of $\approx 3.16$ for amplitude \\
 \reff{ampDec} & direct relation between variations in amplitude and decibels \\
 \reff{periodicidade} & equivalences in a periodic sound with respect to wavelength, frequency and sample rate \\
 \reff{sinusoid} & sample amplitudes in a sinusoid \\
 \reff{sawTooth} & sample amplitudes in a sawtooth wave \\
 \reff{triangular} & sample amplitudes in a triangular wave \\
 \reff{square} & sample amplitude in a square wave \\
 \reff{sampleandoFormaDeOnda} & samples in a sound derived from a sampled wave period \\
 \reff{recomposicaoFourier} & reconstruction of samples from the Fourier components \\
 \reff{moduloEfase} & reconstruction of real samples (e.g. for audio) from Fourier components \\
 \reff{coefsPareados} & number of pairs of Fourier coefficients which are related to the same frequency \\
 \reff{equivalenciasFreqs} & indexes of equivalent frequencies and coefficients for real signals \\
 \reff{equivalenciasModulos} & equal modules between samples of real signals \\
 \reff{equivalenciasFases} & equivalence in phases between samples of real signals \\
 \reff{eq:reconsCompleta} & complete reconstruction of the signal using Fourier components and previous equations \\
 \reff{eq:notaBasica} & sample sequence related to a basic note \\
 \reff{periodoUnico} & sample sequence of a period of an arbitrary waveform \\
 \reff{eq:notaBasicaTimbre} & note samples derived from a sampled waveform \\
 \reff{eq:distOuvidos} & distance of a (sound) source to each ear given the distance between the ears and an (x,y) position of the source \\
 \reff{eq:dti} & Interaural Time Difference (ITD), the time difference of a sound reaching each ear \\
 \reff{eq:dii} & Interaural Intensity Difference (IID), the intensity difference (in decibels) of a sound reaching each ear \\
 \reff{eq:locImpl} & ITD and IID in terms of sample delays and their amplitudes \\
 \reff{eq:angulo} & azimuthal angle of a (x, y) source \\
 \reff{eq:mixagem} & samples that result from mixing sounds \\
 \reff{eq:concatenacao} & samples that result from concatenating sounds \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Equation numbers and their descriptions.
All these equations are implemented in file \texttt{src/sections/3.py}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{eq:lut} & sample sequence generated by means of a lookup table (LUT) \\
 \reff{freqLinear} & frequency at each sample in a linear transition of frequency \\
 \reff{indiceLinear} & indices of a LUT in a linear transition of frequency \\
 \reff{serieAmostralLin} & sample sequence obtained through a LUT in a linear transition of frequency \\
 \reff{freqExponencial} & frequency at each sample in an exponential transition of frequency (linear pitch) \\
 \reff{indiceExponencial} & indices of a LUT in an exponential transition of frequency (linear pitch) \\
 \reff{serieAmostralLog} & sample sequence obtained through a LUT in an exponential transition of frequency \\
 \reff{seqAmp} & amplitude factors at each sample in an exponential transition of amplitude ($\approx$ linear volume) \\
 \reff{transAmp} & sample sequence with an exponential transition of amplitude ($\approx$ linear volume) \\
 \reff{seqAmpLin} & amplitude factors at each sample in a linear transition of amplitude \\
 \reff{seqAmpDB} & sample sequence in an exponential transition of amplitude ($\approx$ linear volume) with difference given in decibels \\
 \reff{eq:conv} & sample sequence obtained through the convolution of two other sequences (e.g. for applying FIR filters) \\
 \reff{eq:diferencas} & difference equation (e.g. for applying IIR filters) \\
 \reff{eq:passa-baixas} & IIR coefficients for a simple, useful and well-behaved low-pass filter \\
 \reff{eq:passa-altas} & IIR coefficients for a simple, useful and well-behaved high-pass filter \\
 \reff{eq:varAux} & auxiliary variables for the following band-pass and band-reject filters \\
 \reff{eq:passa-banda} & IIR coefficients for a simple, useful and well-behaved band-pass filter \\
 \reff{eq:rejeita-banda} & IIR coefficients for a simple, useful and well-behaved band-reject filter \\
 \reff{eq:branco} & Fourier coefficients of a white noise \\
 \reff{eq:rosa} & Fourier coefficients of a pink noise \\
 \reff{eq:marrom} & Fourier coefficients of a brown noise \\
 \reff{eq:azul} & Fourier coefficients of a blue noise \\
 \reff{eq:violeta} & Fourier coefficients of a violet noise \\
 \reff{eq:preto} & Fourier coefficients of a black noise \\
 \reff{vbrGamma} & indices for a vibrato given its frequency and using a LUT \\
 \reff{vbrAux} & samples for applying a vibrato \\
 \reff{vbrF} & frequency at each sample of a sound with vibrato \\
 \reff{vbrGamma2} & indices for LUT in a sound with vibrato \\
 \reff{vbrT} & sample sequence of a sound with vibrato \\
 \reff{trA} & amplitude at each sample for a tremolo \\
 \reff{trT} & sample sequence of a sound with tremolo \\
 \reff{eq:fmEsp} & components in FM synthesis when both modulator and carrier are sines \\
 \reff{eq:Bessel} & the Bessel function \\
 \reff{eq:specAM} & components in AM synthesis when both modulator and carrier are sines \\
 \reff{fmGammaAux} & indices for LUT in modulator of an FM synthesis \\
 \reff{fmAux} & sample sequence of a modulator in an FM synthesis \\
 \reff{fmF} & frequeny at each sample of a sound derived from FM synthesis \\
 \reff{fmGamma} & indices for the final signal in FM synthesis using LUT \\
 \reff{fmT} & sample sequence of a sound generated through FM and using LUT \\
 \reff{amA} & amplitude at each sample in a sound generated though AM \\
 \reff{amT} & sample sequence of a sound generated through AM and using LUT \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Equation numbers and their descriptions.
All these equations are implemented in file \texttt{src/sections/3.py}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{eq:vinculos} & an example of bonds between musical characteristics \\
 \reff{eq:fDoppler} & relation between frequencies and speed in the Doppler effect \\
 \reff{eq:aDoppler} & relation between position, speed and amplitude in the Doppler effect \\
 \reff{eq:ffDoppler} & relation between position, speed and amplitude in the Doppler effect \\
 \reff{eq:p1rev} & samples of a FIR filter for the first period of a reverberation \\
 \reff{eq:p2rev} & samples of a FIR filter for the second period of a reverberation \\
 \reff{eq:rev} & samples of the FIR filter for a reverberation (considering both first and second periods) \\
 \reff{eq:adsr} & amplitude factors for each sample in an ADSR envelope \\
 \reff{eq:adsrApl} & sample sequence of a sound with an ADSR envelope \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Equation numbers and their descriptions.
All these equations are implemented in file \texttt{src/sections/4.py}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{escSim} & perfectly symmetric scales in each octave with the twelve semitones \\
 \reff{eq:escalas} & diatonic scales \\
 \reff{eq:relacaoDia} & the succession of tones and semitones of a diatonic scale \\
 \reff{eq:escalasMenores} & sequences of semitones for the three types minor scales \\
 \reff{eq:serieHarmonica} & harmonic series in terms of semitones \\
 \reff{triades} & triads (chords constituted by thirds) \\
 \reff{eq:rhythmicUnit} & a convention to specify a unit of rhythmic division or agglomeration \\
 \reff{eq:groups} & definition of algebraic groups \\
\end{tabular}
\end{table*}

\clearpage
\section{Figures}\label{sec:lfigures}

\begin{table*}[htp!]
\centering
\caption{Figure numbers and their descriptions.
All these equations are implemented in files \texttt{src/aux/*}.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{fig:PCM} & PCM PCM audio (discrete and digital) samples \\
 \reff{fig:formasDeOnda} & synthetic and sampled waveforms \\
 \reff{fig:espectroDeOndas} & spectrum of basic waveforms \\
 \reff{fig:espectroOboe} & spectrum of a real note and of one derived from one sampled period \\
 \reff{fig:amostras2} & sinusoid represented by two samples \\
 \reff{fig:amostras3} & sinusoid represented by three samples \\
 \reff{fig:amostras4} & sinusoids in 4 samples \\
 \reff{fig:formas4} & basic waveforms within 4 samples \\
 \reff{fig:amostras6} & sinusoids in 6 samples \\
 \reff{fig:formas6} & basic waveforms withing 6 samples \\
 \reff{fig:spac} & ITD and IID (spatial localization cues)\\
 \reff{fig:mixagem} & mixing PCM audio \\
 \reff{fig:concatenacao} & concatenation/juxtaposition of PCM audio \\
 \reff{fig:lut} & Lookup table \\
 \reff{fig:transicao} & transitions of intensity \\
 \reff{fig:conv} & convolution \\
 \reff{fig:delays} & convolution yielding time shifting, multiple time delays, sound amalgam \\
 \reff{fig:iir} & frequency response of useful IIR filters \\
 \reff{fig:ruidos} & spectrum and waveform of noises \\
 \reff{fig:vibrato} & spectrogram of a vibrato \\
 \reff{fig:tremolo} & waveform of a tremolo \\
 \reff{fig:adsr} & ADSR envelope \\
 \reff{fig:movContraponto} & counterpoint movements \\
 \reff{fig:pulsoSubAgl} & musical metric in terms of divisions of temporal units \\
 \reff{fig:climax} & distinctions of musical climax by localization \\
\end{tabular}
\end{table*}

@@

\begin{table*}[htp!]
\centering
\caption{Table numbers and their descriptions.}
\begin{tabular}{ c | p{12cm} }
   Number & Description \\\hline
 \reff{eq:intervalos} & musical intervals, their notations and qualities \\
 \reff{tab:harmonia} & tonal harmonic functions in the major scale \\
 \reff{tab:duracoes} & duration scales yielding perception of pitch and rhythm \\
 \reff{tab:change} & music by permutation of units (change ringing) \\
\end{tabular}
\end{table*}

\clearpage
\section{Scripts}
\subsection{For all equations and relations in each section.}

\begin{table*}[htp!]
\centering
\caption{Script files and their descriptions.}
\begin{tabular}{ c | p{12cm} }
   Filename & Description \\\hline
  \texttt{src/sections/2.py} & implementation of all the equations for the basic note in PCM audio in Section~\ref{sec:discNote} \\
  \texttt{src/sections/3.py} & implementation of all the equations for variations within a note described in Section~\ref{sec:varInternas} \\
  \texttt{src/sections/4.py} & implementation of all the techniques for assembling notes into music described in Section~\ref{sec:notesMusic} \\
\end{tabular}
\end{table*}

\clearpage
\subsection{To render musical pieces}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:discNote}. All files are in the directory \texttt{src/pieces2/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 Reduced-fi & \texttt{reduced-fi.py} & concatenation of simple notes \\
 Sonic pictures & \texttt{quadrosSonoros.py} & mixing of simple notes  \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:internalVar}. All files are in the directory \texttt{src/pieces3/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 ADa and SaRah & \texttt{ADAandSaRah.py} & ADSR envelope \\
 Tremolos, Vibratos and Frequency & \texttt{bonds.py} & bonds between tremolos, vibratos and frequency  \\
 Bella Rugosi & \texttt{bellaRugosi.py} & rugosity achieved through frequencies between 15 adn 30 Hz \\
 Children Choir & \texttt{childChoir.py} & achieving choir sonorities by small variations of the same basic note \\
 Noisy Band & \texttt{noisyBanda.py} & using various noises \\
 ParaMeter Transitions & \texttt{paraMeter.py} & gradual changes of parameters within one note \\
 Little Train of Impulsive Hillbilies~\footnote{This names translates into ``Trenzinho de Caipiras Impulsivos'' which is a pun with the Villa-Lobos' ``Trenzinho do Capira''.} & \texttt{littleTrain.py} & the use of convolution with impulses to achieve rhythm \\
 Shakes and Wiggles & \texttt{shakesWiggles.py} &  tremolos and vibratos \\
\end{tabular}
\end{table*}

\begin{table*}[htp!]
\centering
\caption{Piece names, script files and the concepts they exemplify from Section~\ref{sec:notesMusic}. All files are in the directory \texttt{src/pieces4/}.}
\begin{tabular}{ p{5cm} | p{3.5cm} | p{6.2cm} }
   Name & Filename & Description \\\hline
 Acorde Cedo & \texttt{acordeCedo.py} & chord successions and modulation \\
 Conta Ponto & \texttt{contaPonto.py} & melodic lines conducted within the rules of counterpoint \\
 Crystals & \texttt{crystals.py} & symmetric musical scales \\
 Dirracional & \texttt{dirracional.py} & directional arcs \\
 Intervals & \texttt{intervals.py} & musical intervals \\
 MicroTone & \texttt{microTone.py} & microtonality (the use of intervals smaller than the semitone) \\
 Poly-Hit-My & \texttt{polyHitMy.py} & polyrhythm (multiple metrics at once) \\
\end{tabular}
\end{table*}

\clearpage
\subsection{To render the figures used in the article}
The files \texttt{src/figures/*} render each of the figures (listed above in Section~\ref{sec:lfigures}.

\clearpage
\section{Other documents}
The files in \texttt{latex/*} render the article PDF and this Supporting Information file.

The script \texttt{src/aux/iso226.py} can generate the Equal Loudness Contour as described in its latest revision~\cite{iso226}.

The article is largely based on the MSc dissertation~\cite{dissertacao}.
